Democracy, Public Support, and Measurement Uncertainty

### 2021-04-28 paper/dcpo_demsupport.Rmd
presenting the orginal works in a table in the appendix

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: svm-latex-ms2.tex
title: "Democracy, Public Support, and Measurement Uncertainty"
thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses. In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study. We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion. Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty. [149/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  glue,
  broomExtra, tidyverse, janitor, # data wrangling
  drhutools,
  dotwhisker # visualization
)

@@

```{r dataInput}

@@

```{r claassenAJPS}
# Pooled model -----
# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

@@

df_result_cls <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))

  if (class(result) == "plm") {
    tidy(result, conf.int = TRUE) %>%
      mutate(std.error = vcovBK_se(result),
             n = nobs(result))
  } else{
    tidy(result, conf.int = TRUE) %>%
      mutate(std.error = vcovHC_se(result),
             n = nobs(result))
  }

@@

save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

@@

# References

<div id="refs"></div>

>>>>

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: FALSE
    latex_engine: xelatex
    # template: svm-latex-ms2.tex

title: "Democracy, Public Support, and Measurement Uncertainty"
thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."

# author:
# - name: Yuehong 'Cassandra' Tai
#   affiliation: University of Iowa
# - name: Yue Hu
#   affiliation: Tsinghua University
# - name: Frederick Solt
#   affiliation: University of Iowa

abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses. In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study. We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion. Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty. [149/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  eval = FALSE,
  dpi = 300
)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broomExtra, tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker # visualization
)

@@

```{r dataInput, eval=TRUE}

@@

```{r claassenAJPS, eval=TRUE}
# Pooled model -----
# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

@@

df_result_cls <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

tidy_result_cls <- map(df_result_cls, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

  if (class(result) == "plm") {
     mutate(df_result, std.error = vcovBK_se(result))
  } else{
    mutate(df_result, std.error = vcovHC_se(result))
  }

@@

glance_result_cls <- map(df_result_cls, glance)

#save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

# References  {-}

<div id = 'refs'></div>

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Numeric Results for Replicating @Claassen2020a

```{r cls2020a, results='asis', eval = TRUE}
ls_result_cls <-
  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
    ls_sum <- list(tidy = aTidy,
                   glance = aGlance)

    class(ls_sum) <- "modelsummary_list"

    return(ls_sum)
  })

names(ls_result_cls) <- c("Pooled OLS 1", "Pooled OLS 2", "GMM 1", "GMM 2")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(ls_result_cls, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

# Numeric Results for Replicating @Claassen2020b
